Details of specific functions

### 2018-05-30 inst/gitbook/03_specific-tutorials.Rmd
Merged master into model-test2
# Conflicts:
#	DESCRIPTION
#	NAMESPACE
#	NEWS.md
#	R/adonis.dispRity.R
#	R/boot.matrix.R
#	R/clean.data.R
#	R/dispRity.metric.R
#	R/dispRity.utilities.R
#	R/est.VCV.R
#	R/est.mean.R
#	R/input.param.R
#	R/make.metric.R
#	R/misc.model.test.fun.R
#	R/model.test.R
#	R/model.test.lik.R
#	R/model.test.sim.R
#	R/opt.mode.R
#	R/plot.dispRity.R
#	R/plot.dispRity_fun.R
#	R/print.dispRity.R
#	R/summary.dispRity.R
#	README.md
#	inst/gitbook/03_specific-tutorials.Rmd
#	man/model.test.Rd
#	man/model.test.sim.Rd
#	paper/References.bib
#	paper/dispRity_paper.tex
#	paper/dispRity

One additional important argument is `dimensions` that specifies how many dimensions from the matrix should be used for further analysis.
When missing, all dimensions from the ordinated matrix are used.

@@

>>>>

One other argument is `dimensions` that specifies how many dimensions from the matrix should be used for further analysis.
When missing, all dimensions from the ordinated matrix are used.

@@

It is also possible to specify the sampling probability in the bootstrap for each elements.
This can be useful for weighting analysis for example (i.e. giving more importance to specific elements).
These probabilities can be passed to the `prob` argument individually with a vector with the elements names or with a matrix with the rownames as elements names.
The elements with no specified probability will be assigned a probability of 1 (or 1/maximum weight if the argument is weights rather than probabilities).

```{r, eval=TRUE}
## Attributing a weight of 0 to Cimolestes and 10 to Maelestes
boot.matrix(BeckLee_mat50, prob = c("Cimolestes" = 0, "Maelestes" = 10))
```
